---
title: "Formatting Text"
author: "S.K."
date: '2022-07-22'
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Let's try!

First, italic text
This word is *italic* and not **bold** or regular

## Some embedded code 

Today is `r Sys.Date()`, have a great day!!
The mtcars dataset has `r nrow(mtcars)` rows.


# FRUITS I LOVE

I love fruit. Here are my favorites in no particular order

* Apples
* Mango
* Pineapples
* Watermelon

If you insist, here are my favorite top three in order of preference:

1. Pineapples
1. Mango
1. Watermelon

## WHERE 

Where I learn this stuff? There are many cool places.

For example the [R Markdown: The Definitive Guide](https://bookdown.org/yihui/rmarkdown/documents.html)

I can also publish my cool reports in [RPub](https://www.rpubs.com/)  at *https://www.rpubs.com/* for free

### IRIS

Iris is a pretty flower. The iris dataset has `r nrow(iris)` rows and `r ncol(iris)` columns. 
The iris below belongs to the `r iris$Species[1]` family.

![Iris image](/Users/apple/Google Drive (skuzulugil@gmail.com)/MSC2011H/Iris.jpg)


### Code Chunk

I have a code chunk displaying a dataframe

```{r cute_df, echo=FALSE, paged.print=TRUE}
knitr::kable(head(iris), digits = 2)
```

### Some table

What we have done so far...

|Subject|Package|Function|
|:------|-------:|:-------:|
|Plotting|ggplot2|ggplot|
|format tables|knitr|kable|
|Manipulate data|dplyr|all functions|


And it was fun...


## Test Different Language

A little bash code to list all R files 

```{bash dir_list}
ls -lh *.R
```

And a little python snippet

```{python hello, eval=FALSE, echo=TRUE}
x = 'hello, python world!‘
print(x.split(' '))
```

```{r show_query}
library(dplyr)
a <- mtcars %>% filter(mpg > 15) %>% select(fuel=mpg, hp) %>% collect()
show_query(a)
```
